A Prediction of the 2024 U.S. Election

### 2024-11-04 paper/paper.qmd
appendix b

@@

Sample survey could find here: 
[Surey Link ](https://docs.google.com/forms/d/e/1FAIpQLSd_yZTdfVJpPJY0ItPLdJ1xwtL0zQiGmBf8KE_lCJfoy2lJCQ/viewform?usp=sf_link).

>>>>

### Sample Survey
Google Forms will be used to collect data efficiently and securely, ensuring no information is leaked. The survey will cover aspects such as gender, race, demographics, education, first-choice candidate, and views on the current United States.

A complete sample survey could be found in the following link https://forms.gle/1jrQP7bPqntJ9N2s9 or by clicking [Sample survey ](https://docs.google.com/forms/d/e/1FAIpQLSd_yZTdfVJpPJY0ItPLdJ1xwtL0zQiGmBf8KE_lCJfoy2lJCQ/viewform?usp=sf_link).

Proposed Survey Questions:

1. What sex were you assigned at birth, or on your original birth certificate?
- Male
- Female

2. How do you currently describe your gender?
- Male
- Female
- Transgender
- Non-binary
- other

3. What is your racial self-identification?
- White
- Black
- Asian
- Indigenous
- Prefer not to say
- Other

4. What is your current age?
- Under 18
- 30-45
- 46-51
- 52-66
- over 66

5. What is your highest level of education?
- High school or Under
- Undergraduate
- Graduate
_ Doctor

6. Which  candidate would you vote for in U.S. 2024 Presidential Election?
- Donald Trump (Republic)
- Kamala Harris (Democrat)
- Other

7. Would you vote for the 2024 U.S. Presidential Election?
- Yes
- No
- I'm not sure

8. Are you satisfied with the current situation in the United States?
- Pretty much
- Somewhat satisfied
- Neutral
- Somewhat dissatisfied
- Very Dissatisfied
- No opinion

9. What is your most concerned toward to current U.S?
- Economy
- Employment
- Education
- Environment
- Diplomacy
- Immigration
- Domestic safety

@@
